Using numerical modelling to investigate temperature and wave exposure as drivers

### 2019-10-09 morphology_paper.Rmd
similar adjustments made to wave plot as per previous commit. Also adjusted p label position in both wave boxplots.

wave_plot_1 <- ggplot(data = abio_clim, aes(x = site, y = hs_mean)) +
  geom_point(show.legend = FALSE, shape = 17, size = 2) + 
  scale_x_discrete(limits = positions_wave) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5)) +
  geom_errorbar(aes(x = site, ymin = hs_mean - hs_sd, ymax = hs_mean + hs_sd)) + 
  xlab("") + 
  ylab("") + 
  theme(legend.position = "none") + 
  theme(plot.title = element_text(hjust = 0)) + 
  coord_flip() + 
  theme_bw()

wave_plot_2 <- ggplot(data = abio_clim, aes(x = site, y = tp_mean)) +
  geom_point(show.legend = FALSE, shape = 16, size = 2) + 
  scale_x_discrete(limits = positions_wave) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5)) +
  geom_errorbar(aes(x = site, ymin = tp_mean - tp_sd, ymax = tp_mean + tp_sd)) + 
  xlab("") + 
  ylab("") + 
  theme(legend.position = "none") + 
  theme(plot.title = element_text(hjust = 0)) + 
  coord_flip() +
  theme_bw()

wave_boxplot_1 <- ggplot(data = wave_ann_meta, aes(x = region, y = hs_mean, fill  = region)) + 
  geom_boxplot(show.legend = FALSE) + 
  stat_compare_means(label.y =0.5 ,label.x = 2.5, label = "p.format") + 
  xlab("") + 
  ylab("") + 
  coord_flip() + 
  theme_bw() +
  scale_fill_grey(start = 0.4, end = 0.8)

wave_boxplot_2 <- ggplot(data = wave_ann_meta, aes(x = region, y = tp_mean, fill  = region)) + 
  geom_boxplot(show.legend = FALSE) + 
  stat_compare_means(label.y = 8.1, label.x = 2.5, label = "p.format") + 
  xlab("") + 
  ylab("") +
  ylim(8,12) + 
  coord_flip() + 
  theme_bw() +
  scale_fill_grey(start = 0.4, end = 0.8)

>>>>

wave_plot_1 <- ggplot(data = abio_clim, aes(x = site, y = hs_mean)) +
  geom_point(show.legend = FALSE, shape = 17, size = 2) + 
  scale_x_discrete(limits = positions_wave) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5)) +
  geom_errorbar(aes(x = site, ymin = hs_mean - hs_sd, ymax = hs_mean + hs_sd)) + 
  xlab("") + 
  ylab("") + 
  theme(legend.position = "none") + 
  coord_flip() + 
  theme_bw() + 
  theme(axis.text.y=element_text(vjust=0.3))

wave_plot_2 <- ggplot(data = abio_clim, aes(x = site, y = tp_mean)) +
  geom_point(show.legend = FALSE, shape = 16, size = 2) + 
  scale_x_discrete(limits = positions_wave) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5)) +
  geom_errorbar(aes(x = site, ymin = tp_mean - tp_sd, ymax = tp_mean + tp_sd)) + 
  xlab("") + 
  ylab("") + 
  theme(legend.position = "none") + 
  coord_flip() +
  theme_bw() + 
  theme(axis.text.y=element_text(vjust=0.3))

wave_boxplot_1 <- ggplot(data = wave_ann_meta, aes(x = region, y = hs_mean, fill  = region)) + 
  geom_boxplot(show.legend = FALSE) + 
  stat_compare_means(label.y =0.6 ,label.x = 2.5, label = "p.format") + 
  xlab("") + 
  ylab("") + 
  coord_flip() + 
  theme_bw() +
  scale_fill_grey(start = 0.4, end = 0.8) + 
  theme(axis.text.y=element_text(vjust=0.3))

wave_boxplot_2 <- ggplot(data = wave_ann_meta, aes(x = region, y = tp_mean, fill  = region)) + 
  geom_boxplot(show.legend = FALSE) + 
  stat_compare_means(label.y = 8.2, label.x = 2.5, label = "p.format") + 
  xlab("") + 
  ylab("") +
  ylim(8,12) + 
  coord_flip() + 
  theme_bw() +
  scale_fill_grey(start = 0.4, end = 0.8) + 
  theme(axis.text.y=element_text(vjust=0.3))
